3.5: Causal Inference and DAGs - R Practice

### 2019-11-07 content/r/17-r-practice.Rmd
Fix link to practice 17, fix webpage for practice 17

---
title: "3.3 OLS: Model Specification Strategies - R Practice"
editor_options: 
  chunk_output_type: console
---

@@

```{r, fig.retina=3}
dagify(Y~X+Z,
       X~Z,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=1)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r, fig.retina=3}
dagify(Y~X+M,
       M~X,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=1)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r, fig.retina=3}
dagify(Y~X+Z+B,
       Z~B+A,
       X~A,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=1)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r, fig.retina=3}
dagify(Y~X+B+C,
       Z~B+A,
       X~A,
       C~X,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=2)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r, fig.retina=3}
dagify(Y~X+Z+A,
       Z~X+A+B,
       B~A,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=2)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r}
library(corrplot)
bwght %>%
  select(bwght, cigs, faminc, cigprice, motheduc) %>%
  cor(., use="pairwise.complete.obs")
```

@@

```{r}
library(ggdag)
dagify(bwght~cigs+inc,
       cigs~price+educ+inc,
       inc~educ,
       exposure = "cigs",
       outcome = "bwght") %>% 
  ggdag(stylized = FALSE, seed=1)+theme_dag_blank()+theme(legend.position = "none")
```

@@

- For independencies $(x \perp y)$: run a regression of $y$ on $x$.
- For *conditional* independencies $(x \per y | z, a)$: run a regression of $y$ on $x, z, a$.

@@

```{r}
lm(bwght~motheduc+cigs+faminc, data = bwght) %>% summary()
```

```{r}
lm(bwght~cigprice+cigs+faminc, data = bwght) %>% summary()
```

```{r}
lm(motheduc~cigprice, data = bwght) %>% summary()
```

```{r}
lm(faminc~cigprice, data = bwght) %>% summary()
```

@@

## Question 11
Test these implications appropriately, like you did in Question 5.

```{r}
lm(bwght~cigprice+cigs+motheduc+faminc, data = bwght) %>% summary()
```

```{r}
lm(motheduc~cigprice, data = bwght) %>% summary()
```

Does this model hold up well?

>>>>

---
title: "3.5: Causal Inference and DAGs - R Practice"
editor_options: 
  chunk_output_type: console
---

@@

```{r, echo=F, fig.retina=3}
dagify(Y~X+Z,
       X~Z,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=1)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r, echo=F, fig.retina=3}
dagify(Y~X+M,
       M~X,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=1)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r, echo=F, fig.retina=3}
dagify(Y~X+Z+B,
       Z~B+A,
       X~A,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=1)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r, echo=F, fig.retina=3}
dagify(Y~X+B+C,
       Z~B+A,
       X~A,
       C~X,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=2)+theme_dag_blank()+theme(legend.position = "none")
```

@@

```{r, echo=F, fig.retina=3}
dagify(Y~X+Z+A,
       Z~X+A+B,
       B~A,
       exposure = "X",
       outcome = "Y") %>% 
  ggdag(stylized = FALSE, seed=2)+theme_dag_blank()+theme(legend.position = "none")
```

@@

@@

```{r, echo=T}
library(ggdag)
dagify(bwght~cigs+inc,
       cigs~price+educ+inc,
       inc~educ,
       exposure = "cigs",
       outcome = "bwght") %>% 
  ggdag(stylized = FALSE, seed=1)+theme_dag_blank()+theme(legend.position = "none")
```

@@

- For independencies $(x \perp y)$: run a regression of $y$ on $x$.
- For *conditional* independencies $(x \perp y | z, a)$: run a regression of $y$ on $x, z, a$.

@@

@@

## Question 11
Test these implications appropriately, like you did in Question 5. Does this model hold up well?
